---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

**NOTE: these are some basic functions that I find useful, they are currently under very gradual development and do not perform extensive (or any) error checks on inputs, basic help pages are provided.**

# bioUtils

<!-- badges: start -->
<!-- badges: end -->

The goal of bioUtils is to provide easy distribution and implementation of some basic time saving functions that I have found usefull.

## Installation

You can install the development version of bioUtils from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("smallwerke/bioUtils")
```

## MAN pages

I will be trying to keep the manual pages for each function relatively up to date and helpful. Please refer to / access them 

```{r help}
library(bioUtils)
help(CTtoRE, package=bioUtils)
```

# CTtoRE

This function is designed to accept data in tibble form that was generated by the [RQdeltaCT](https://cran.r-project.org/web/packages/RQdeltaCT/vignettes/my-vignette.html) package. The idea is for you to load your CT values in using RQdetlaCT, perform desired QC with that package and pass the tibble of desired genes & samples off to this function which will use RQdeltaCT calls to determine the deltaCT, 2^-(delta delta CT), and the relative expression values based off of the housekeeping gene and control group that is specified.

Typically the missing (Undtermined) values will be replaced by their group mean for calculation purposes in the RQdeltaCT script in order for most of the features to function. This can be misleading when loading the data into a figure in R or Prism or whatever that displays all individual data points. Setting them to NA is an option when calculating the relative expression values.

If you supply an optional argument containing your initial CT values as loaded by RQdeltaCT then all results that had an ***Undetermined*** value will be set to 'NA' in a separate RE tibble in the return data for easier loading into R.

A tibble containing two lists and three to four tibbles is returned.
