---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

**NOTE: these are some basic functions that I find useful, they are currently under very gradual development and do not perform extensive (or any) error checks on inputs, basic help pages are provided.**

# bioUtils

<!-- badges: start -->
<!-- badges: end -->

The goal of bioUtils is to provide easy distribution and implementation of some basic time saving functions that I have found usefull.

## Installation

You can install the development version of bioUtils from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("smallwerke/bioUtils")
```

## MAN pages

I will be trying to keep the manual pages for each function relatively up to date and helpful. Please refer to / access them 

```{r help}
library(bioUtils)
help(CTtoRE, package=bioUtils)
```

# CTtoRE

This function is designed to accept data in tibble form that was generated by the [RQdeltaCT](https://cran.r-project.org/web/packages/RQdeltaCT/vignettes/my-vignette.html) package. The idea is for you to load your CT values in using RQdetlaCT, perform desired QC with that package and pass the tibble of desired genes & samples off to this function which will use RQdeltaCT calls to determine the deltaCT, 2^-(delta delta CT), and the relative expression values based off of the housekeeping gene and control group that is specified.

A tibble containing two lists and three tibbles is returned.
